\Ace: Growing a Statically-Typed Language Inside a Python

### 2013-11-16 ace-pldi14/ace-pldi14.tex
Added FP example code

But Ace has proven useful for more than low-level tasks like programming a GPU with OpenCL. We now describe several interesting extensions that implement semantics of primitives drawn from a range of different language paradigms, to justify our claim that these mechanisms are highly expressive.

\subsection{Growing a Statically-Typed Python Inside an Ace}
Ace comes with a target, base and type implementing Python itself: \verb|ace.python.python|, \verb|ace.python.base| and \verb|ace.python.dyn|. These can be supplemented by additional active types and used as the foundation for writing actively-typed Python functions. These functions can either be compiled ahead-of-time to an untyped Python file for execution, or be immediately executed with just-in-time compilation, just like the OpenCL examples we have shown. Some of the examples in the next section support this target in addition to the OpenCL target we have focused on thus far.

>>>>

But Ace has proven useful for more than low-level tasks like programming a GPU with OpenCL. We now describe several interesting extensions that implement the semantics of primitives drawn from a range of different language paradigms, to justify our claim that these mechanisms are highly expressive.

\subsection{Growing a Statically-Typed Python Inside an Ace}
Ace comes with a target, base and type implementing Python itself: \verb|ace.python.python|, \verb|ace.python.base| and \verb|ace.python.dyn|. These can be supplemented by additional active types and used as the foundation for writing actively-typed Python functions. These functions can either be compiled ahead-of-time to an untyped Python file for execution, or be immediately executed with just-in-time compilation, just like the OpenCL examples we have shown. Many of the examples in the next section support this target in addition to the OpenCL target we have focused on thus far.

\subsection{Functional Datatypes}
\begin{codelisting}
\lstinputlisting{datatypes_t.py}
\caption{x.}
\label{datatypest}
\end{codelisting}
\begin{codelisting}
\lstinputlisting{datatypes.py}
\caption{y.}
\label{datatypes}
\end{codelisting}
HAIOADJASDASD
